% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\usepackage{hyperref}
\begin{document}

\name{Taylor Fahlman}
\address{(503)-758-6952, fahlmantaylor@gmail.com}
\address{tfahl.com, github.com/fahlmant, irc: recyclops/fahlmant on freenode}
\begin{resume}
 
\section{EDUCATION}
                    {\sl Bachelor of Science,} Computer Science, Simulation Development \\
                    {\sl Bachelor of Art,} Music, Vocal Performance \\
                    Oregon State University\\
                    Current GPA: 3.56\\
                    Expected Graduation Date: June 2017 
                    
                    Corbett High School,
                    Graduated with Honors\\
                    GPA: 3.8\\
                    2009-2012
\section{SKILLS}
                    C/C++, Python, Java, x86 ASM, Git, GitHub, Bash, Chef, Cfengine, Apache, Ganeti, Bacula, rdiff-backup,
                    Nagios, Flask, ReStructured Text, Heiroglyph, Lilypond, Linux, POSIX API
\section{EXPERIENCE}
                    {\sl Student System Administrator} \hfill January 2015-Present \\
                    Open Source Lab, 
                    Corvallis, OR
                    \begin{itemize}  \itemsep -2pt % reduce space between items
                       \item Placeholder
                    \end{itemize}
 
                    {\sl Student IT Worker} \hfill September 2013-June 2015 \\
                    School of Civil and Construction Engineering, OSU, 
                    Corvallis, OR 
                    \begin{itemize}  \itemsep -2pt %reduce space between items
                       \item Helped manage computer labs and graduate systems. Deployed software via SCCM.
                    \end{itemize} 

                    {\sl Intro to Computer Science I \& II Teaching Assistant} \hfill January 2014-January 2015\\
                    School of EECS, OSU
                    Corvallis, OR
                    \begin{itemize}  \itemsep -2pt %reduce space between items
                        \item Taught students C/C++, and basic programming concepts.
                    \end{itemize}
                    
                    {\sl Creative Media Specialist} \hfill February 2013 - June 2013 \\
                    College of Forestry, OSU,
                    Corvallis, OR
                    \begin{itemize}
                       \item Created promotional videos.
                    \end{itemize} 
 
\section{COMMUNITY \\ SERVICE}  
                {\sl Trout Creek Bible Camp\\}
                    Volunteered 6 full 10-week summers.
                    Cleaned dishes, bathrooms, construction projects,
                    led between 8 - 12 campers each week,
                    created 5 videos of the week's activities,
                    led 20 staff members, overseeing their daily jobs.

                {\sl Key Club\\}
                    Raised money for March of Dimes and UNICEF, held an annual Pancake breakfast
                    for Veterans, participated in the Adopt-a-Road program.
                    \begin{itemize}  \itemsep -2pt % reduce space between items
                        \item Member 2010-2011
                        \item President 2011-2012
                    \end{itemize}

\section{OTHER\\}             
            Elected {\it Historian}, Antioch Men's Co-op, OSU. \\
            Taught Python \href{https://github.com/fahlmant/LessonsForMusicMajors}{(slides.tfahl.com)} to Music Majors. \\
            Created a music generation \href{http://music.tfahl.com}{(music.tfahl.com)} 
            site using Flask and Python for rhythm practice,
            and released the code \href{https://github.com/fahlmant/RhythmGenerator}{(github.com/fahlmant/RythmGenerator)}.\\
            OSU Chamber Choir, September 2014-Present\\
            OSU Honor Roll, 2013: Winter, 2014: Winter, Spring, Fall, 2015: Winter, Spring\\

\end{resume}
\end{document}
